Analyzing DECREASE trials for extent of data fabrication

### 2016-03-11 submission/manuscript.Rmd
Add initial meta-analysis models for step 1

bouri_data$ln_rr <- log((bouri_data$d/(bouri_data$b+bouri_data$d))/(bouri_data$c/(bouri_data$a+bouri_data$c)))
bouri_data$se_ln_rr <- sqrt((1/bouri_data$a)+(1/bouri_data$b)+(1/bouri_data$c)+(1/bouri_data$d))
```

>>>>

bouri_data$ln_rr <- log((bouri_data$d/(bouri_data$b+bouri_data$d))/(bouri_data$c/(bouri_data$a+bouri_data$c)))
bouri_data$se_ln_rr <- sqrt((1/bouri_data$a)+(1/bouri_data$b)+(1/bouri_data$c)+(1/bouri_data$d))

mod_clean <- metafor::rma(yi = ln_rr,
             sei = se_ln_rr,
             method = "REML",
             data = bouri_data[bouri_data$decrease == 0, ],
             weighted = TRUE)
mod_dirty <- metafor::rma(yi = ln_rr,
             sei = se_ln_rr,
             method = "REML",
             data = bouri_data[bouri_data$decrease == 1, ],
             weighted = TRUE)
```
